The Globular Cluster System of the Auriga Simulations

### 2019-06-03 AurigaGCS.tex
Some updates to introduction

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. The globular cluster systems (GCS) of
the Milky Way (MW) and the Andromeda galaxy (M31) have been studied extensively 
over the last decades. More recent analyses of the Gaia data shed new light on the 
chemical- and structural properties, and on the phase-space distribution 
of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 2018ApJ...859L..13B,
2019A&A...621A..56P, 2019MNRAS.484.2832V}. Moreover, the visbility and ubiquity
of GCs makes it possible to obtain integrated properties of GCs within the Local 
Group with reasonable certainty, and even beyond the Local Group \citep[e.g.][]{1991ARA&A..29..543H}.

The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies \citep[see][for a recent review]
{2006ARA&A..44..193B}. In theory, this information should be readily available
and easily observable in the low redshift Universe, given that GCs survive nearly
a Hubble time of evolution within the violent galactic environments they live in. 
However, these long and complex evolution histories themselves impose their
imprints onto the GCs observables. Thus, a prerequisite to infer galactic histories
from studies of GC systems is to understand the subtleties of the GC formation
and evolution itself.

One important ingredient for plausible formation mechanisms comes from observed 
bimodality in the colour distribution, believed to be indicative of bimodality
in the underlying metallicity distribution of GC systems. GCs in the MW can 
be split up into a metal-rich (red) disk, and a metal-poor (blue) halo
(sub)population. The exact dividing value slightly differs between authors,
e.g. [Fe/H]~$=-0.8$ \citep[according to][]{1985ApJ...293..424Z}, or
[Fe/H]~$=-1.0$ \citep[according to][]{Harris2001}, and may also differ between
\newpage
galaxies \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L,
2006ApJ...639...95P}. It has long been debated whether the Andromeda GCS metallicity 
distribution is uni- bi- or multimodal, with \citet{2016ApJ...824...42C} recently
arguing that the data favours three groups (split at [Fe/H] $= -0.4$ and $-1.5$)
after more accurate age-measurements improved classification of star clusters
as globular (or otherwise).

The literature offers several formation scenarios.

@@

In a recent study, Chiou et al. speculate that GCs may form in supersonically
induced gasseous objects at high redshifts. These objects are free of dark matter 
and populate a mass range consistent with the typical mass scale of GCs. 
Interestingly, the authors find present-day absolute visual magnitude and 
characteristic scales consistent with GCs in the Local group, based on a 
rudimentary star formation model.

@@

\todo[inline]{Paragraph: narrow down to this work}
\begin{itemize}
    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
    \item Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way (or Andromeda).
    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons. First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters. Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations. The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations. Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations. Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy. This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population. Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
\end{itemize}

>>>>

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. The GC system of the Milky Way (MW) consists
of $\sim$160 GCs, most of which are older than $\sim$10~Gyr, and the Andromeda 
galaxy (M31) hosts roughly twice as many GCs with ages $\geq 6$~Gyr. With masses of 
$10^{4-6}$ M\Sun within typical half-mass radii of a few parsec, the combined stellar 
light emitted by GCs makes it possible to obtain integrated properties within the Local
Group with reasonable certainty, and even allows for observations beyond the Local Group 
\citep[e.g.][]{1991ARA&A..29..543H}. The extensive literature on GCs is summarised in
several books and review articles \citep[e.g.][]{Harris2001, 2004Natur.427...31W, 
2006ARA&A..44..193B, 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}, and
recent analyses of the Gaia data shed new light on the chemical- and structural properties,
and on the phase-space distribution of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 
2018ApJ...859L..13B, 2019A&A...621A..56P, 2019MNRAS.484.2832V}.

\todo[inline]{Correlations between GC systems and their host galaxies}
The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies \citep[see][for a recent review]
{2006ARA&A..44..193B}. In theory, this information should be readily available
and easily observable in the low redshift Universe, given that GCs survive nearly
a Hubble time of evolution within the violent galactic environments they live in. 
However, these long and complex evolution histories themselves impose their
imprints onto the GCs observables. Thus, a prerequisite to infer galactic histories
from studies of GC systems is to understand the subtleties of the GC formation
and evolution itself.

The literature offers a wealth of formation channels, most of which can be broadly
classified as ex situ, or as in situ scenarios. In the former picture, GCs form 
in smaller, more metal-poor progenitors that are accreted in subsequent mergers,
as can naturally be expected in the framework of hierarchical galaxy formation
\citep[e.g.][]{1978ApJ...225..357S, 1984ApJ...277..470P}, and Rosenblatt et al. 1988; 
Cen 2001; Bromm \& Clarke 2002; Diemand et al. 2005; Moore et al. 2006; Boley et al. 2009;
Griffen et al. 2010; Trenti et al. 2015; Kimm et al. 2016; Ricotti et al. 2016;
Boylan-Kolchin 2017; Creasey et al. 2019. As for in situ scenarios,
\citet{1985ApJ...298...18F} propose that thermal instabilities in the collapsing
proto-galaxy may lead to GC formation, \citet{1992ApJ...384...50A, 2010ApJ...718.1266M,
2018MNRAS.480.2343C} suggest that GC formation is triggered by (major) gas-rich
galaxy-galaxy mergers and/or interactions, and \citet{2005ApJ...623..650K} envision
GCs to form in the cores of supergiant molecular clouds located within gaseous disks
of (high-redshift) galaxies.

Another broad distinction between formation mechanisms are models that rely on 
special conditions in the early Universe, or those that test the hypothesis that
GC formation at high redshift is governed by the same physical processes of young 
massive clusters \citep[see][for a review]{2010ARA&A..48..431P} in the Local
Universe, where differences arise as the result of nearly a Hubble time of
(dynamical) evolution. This (latter) scenario is extensively tested in the recent
E-MOSAICS project \citep{2018MNRAS.475.4309P, 2019MNRAS.486.3134K}, which 
comprises a suite of cosmological zoom simulations of MW-like galaxies. As for
the former category, \citet{2017Ap&SS.362..183R} investigate what fraction of 
(multiple) stellar populations ends up in bound star clusters after their
formation in gravitationally unstable expanding supershells, which arise from
hypernova explosions of massive pop. III stars. \citet{2019arXiv190408941C} 
speculate in a recent study that GCs may form in supersonically induced gasseous 
objects at high redshifts, and \citet{2019arXiv190508951M} propose that high speed
collisions leave cooling gas without their DM subhaloes which could form GC 
populations that can reproduce the observed $N_{\text{GC}}-M_{\text{vir}}$
correlation \citep[e.g.][]{2019arXiv190100900B} with bimodal metallicity
distributions and ages consistent with observations.

One important constraint on plausible formation mechanisms comes from observed 
bimodality in the colour distribution of most galaxies, believed to be indicative 
of bimodality in the underlying metallicity distribution of GC systems. GCs in
the MW can indeed be split up into a metal-rich (red), and a metal-poor (blue) 
(sub)population. The former group is associated to the galactic disk because it
is a flattened, rotating population found at radii smaller than solar. The latter,
on the other hand, is more radially extended, more populated (with three times
more blue than red GCs), and may be $\leq 1.5$~Gyr older \citep{2005AJ....130..116D}. 
The exact dividing metallicity slightly differs between authors, e.g.
[Fe/H]~$=-0.8$ \citep[according to][]{1985ApJ...293..424Z}, or
[Fe/H]~$=-1.0$ \citep[according to][]{Harris2001}, and may also differ between
galaxies \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L,
2006ApJ...639...95P}. In contrast, it has long been debated whether the Andromeda 
GCS metallicity distribution is uni- bi- or multimodal, and \citet{2016ApJ...824...42C}
argue that the data favours three groups (split at [Fe/H] $= -0.4$ and $-1.5$)
after more accurate age-measurements improved classification of star clusters
as globular (or otherwise). Moreover, the Andromeda GCS has $2-3$ times as many
GCs at large radii, believed to be indicative of a more rich merger history.

@@

@@

\todo[inline]{Paragraph: narrow down to this work}
The star formation model implemented in the Auriga simulations is capable of 
producing realistic Milky Way-like (spiral disk) galaxies at redshift zero. Therefore 
the question naturally arises whether or not the Auriga simulations also produce
a subset of star particles (GC candidates) which is consistent with the GC system
of the Milky Way and/or the Andromeda galaxy (M31). The typical mass scale of 
globular clusters is comparable to the numerical (mass) resolution of cosmological 
zoom simulations. The detailed physics of GC formation in the Universe appears in
observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass 
resolution of $10^{3-5}$ M\Sun in the Auriga simulations. Globular clusters can 
therefore serve as an ultimate test to the star formation model that is implemented 
in the numerical simulations. Moreover, cosmological zoom simulations provide a
detailed (formation and merger) history of the simulated galaxies. This is 
important because theoretical paradigms for globular cluster formation in the 
literature know two distinct classes of GCs that are separated by their exact 
formation sites: an in situ versus an accreted population. Cosmological zoom 
simulations uniquely allow for an investigation into globular cluster formation 
with a particular focus on the properties of the in situ versus accreted subpopulations.
